\Title

### 2021-07-16 manuscript/content.tex
Make small edits (#164)

The type of source is most commonly a point mass for gravity or dipole for
magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
li2020} and tesseroids \citep{bouman2016} have also been used successfully.
In fact, even point sources with a simple inverse distance function, instead of
actual gravity or magnetic fields, can be used as
equivalent sources \citep{cordell1992}.

@@

We performed a similar experiment to one in section~\ref{sec:window_size} but
this time kept the window size fixed to \BoostOverlappingWindowSize{} and
varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
All other experimental procedures remained unchanged.
Fig.~\ref{fig:gradient-boosted-comparison}b shows the RMS error and
Fig.~\ref{fig:gradient-boosted-comparison}d shows the computation time
required for estimating the source coefficients, both as functions of
the window overlap.

@@

We start the interpolation process by defining a set of block-averaged sources
using a block size of 1.8\km{}, resulting in a total of
\AustraliaEqlNSources{}~point sources.
The block size was chosen to match the desired resolution of the final grid
(1~arc-minute is approximately 1.8\km{} at the equator).
Based on the results obtained in Section~\ref{sec:synthetic_distributions}, we
have chosen to use the \emph{relative depth} strategy.
The window overlap was once again fixed at 50\%.
To determine the size of the windows, we computed the amount of computer memory
needed to store the largest Jacobian matrix for different values of window size
(Fig.~\ref{fig:australia-memory-cv-error}a).
We have chosen a size of \AustraliaEqlWindowSize{} in order to limit the
amount of memory needed to under 16~Gigabytes.

>>>>

The most commonly used type of source is a point mass for gravity or dipole for
magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994,
siqueira2017}.
However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
li2020} and tesseroids \citep{bouman2016} have also been used successfully.
In fact, even point sources with a simple inverse distance function, instead of
actual gravity or magnetic fields, can be used as
equivalent sources \citep{cordell1992}.

@@

We performed a similar experiment to the one in section~\ref{sec:window_size}
but this time kept the window size fixed to \BoostOverlappingWindowSize{} and
varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
All other experimental procedures remained unchanged.
Fig.~\ref{fig:gradient-boosted-comparison}b shows the RMS error and
Fig.~\ref{fig:gradient-boosted-comparison}d shows the computation time
required for estimating the source coefficients, both as functions of
the window overlap.

@@

We start the interpolation process by defining a set of block-averaged sources
using a block size of 1.8\km{}, resulting in a total of
\AustraliaEqlNSources{}~point sources.
The block size was chosen to match the desired resolution of the final grid
(1~arc-minute is approximately 1.8\km{} at the equator).
Based on the results obtained in Section~\ref{sec:synthetic_distributions}, we
have chosen to use the \emph{relative depth} strategy.
The window overlap was once again fixed at 50\%.
To determine the size of the windows, we calculated the amount of computer memory
needed to store the largest Jacobian matrix for different values of window size
(Fig.~\ref{fig:australia-memory-cv-error}a).
We have chosen a size of \AustraliaEqlWindowSize{} in order to limit the
amount of memory needed to under 16~Gigabytes.
